%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage{fancyhdr}
\pagestyle{fancy}
% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.9]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Vishwesh}{Jainkuniya}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{The LNMIIT}{302031 Jaipur}{India}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+91 9571355996}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{jainkuniya@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{vishwesh3.github.io}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2015--2019 (Expected)}{B.Tech in Computer Science}{The LNM Institute of Information Technology}{Jaipur, India}{\textit{CGPA:- 7.59 (Till 4th semester)}}{}

\cventry{2013--2015}{Senior Secondary-CBSE AISSCE}{DAV Public School}{Kota, India}{\textit{90\%}}{}

\cventry{2013}{Secondary-CBSE AISSE}{ST. Pauls Sr. Secondary School}{Pratapgarh, Rajasthan, India}{\textit{CGPA:- 9.4}}{}

\section{Experience}
%\subsection{Vocational}
\cventry{May 17 - Ongoing }{\href{https://github.com/zulip/zulip-mobile/graphs/contributors}{\color{blue}https://github.com/zulip/zulip-mobile}}{Google Summer of Code ' 17}{Work from Home}{}{%
\begin{itemize}%
\item Selected under {\href{https://github.com/zulip}{\color{blue}Zulip}}. Worked on a React-Native project.
\end{itemize}}


\cventry{Jun 16 - Aug 16 }{\href{http://bit.ly/mr-hot-app}{\color{blue}https://play.google.com/store/apps/details?id=mrhot.com.mrhot}}{Mr Hot - Android Developer}{Work from Home}{}{Developed an android app for online food ordering from scratch.%
\begin{itemize}%
\item Features implemented :- Online and offline food ordering, refer \& earn, manage account, payment gateway, push notifications for updates and offers, login/sign up/Reset password, app for admin to track orders, live update of item and offers, manage address (add, edit, delete), recharge wallet. 
\end{itemize}}

\cventry{Oct 16 - Nov 16}{\href{http://bit.ly/liveunite}{\color{blue}https://play.google.com/store/apps/details?id=com.liveunite}}{LiveUnite - Android Developer}{Work from Home}{}{Developed android app from scratch to unite with nearby people.%
\begin{itemize}%
\item Features Implemented :- Photo/Video upload, get feeds from nearby people, adjust distance and age, locate on google map, manage and create new account, facebook login. .
\end{itemize}}

\section{Projects}
\cventry{April 16 - May 16}{\href{http://bit.ly/college-plus}{\color{blue}https://play.google.com/store/apps/details?id=lnmiit.madclub.collegeplus}}{College Plus - Android App}{}{}{
\begin{itemize}%
\item Keep track on all your upcoming events. Get lecture details, mess menu, bus timetable. Get reminders to return library books (calculate fine if applicable). Auto update data. Get notified on data updation.  
\end{itemize}}

\cventry{Jun 16}{\href{http://bit.ly/udhaar-app}{\color{blue}https://play.google.com/store/apps/details?id=com.zriton.udhaar}}{Udhaar - Android App}{}{}{
\begin{itemize}%
\item It is one-stop destination for all financial transactions with friends or colleagues. Get reminders for dues. Send an gentle reminder on a single click. Graphical representation of transactions.
\end{itemize}}

\cventry{Feb 17}{\href{https://play.google.com/store/apps/details?id=com.jainkuniya.wimator}{\color{blue}https://play.google.com/store/apps/details?id=com.jainkuniya.wimator}}{Wimator - Android App}{}{}{
\begin{itemize}%
\item With Wimator, captive portal can be easily automated. Auto login when device gets connected to enabled WiFi network. Auto log off when WiFi strength becomes low (threshold value). Get details of previously connected WiFi network's. Perform actions from widget. Manage WiFi networks.
\end{itemize}}

\cventry{Arp 17}{\href{https://github.com/vishwesh3/central-medic-center}{\color{blue}https://github.com/vishwesh3/central-medic-center}}{Central Medic Center - Java Project}{}{}{
\begin{itemize}%
\item Central Medic Center is a Hospital Administration System made for our 'OOP with JAVA' course project. Technologies used are : Java, JSP, MySQL, HTML, CSS, Bootstrap, jQuery and Apache Tomcat.
\end{itemize}}


\section{Computer skills}
\cvitem{Mobile Applications and Analytics}{Android Application Development, iOS(React-Native)}
\cvdoubleitem{Database}{MySql, SQLite}{OS}{Linux, Windows, Mac}
\cvdoubleitem{Languages}{JAVA, Javascript(Beginner), PHP}{VCS}{git}
\cvdoubleitem{Designing}{Adobe Photoshop}{Cloud Computing}{Google cloud engine}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\rfoot{Last updated on
\today}

\clearpage
\end{document}


%% end of file `template.tex'.
